{\steve}: A hierarchical Bayesian model for Supernova Cosmology

### 2018-12-20 papers/methods/paper.tex
Updating PGM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib,manuscript]{emulateapj}

@@

%\usepackage{lineno}
%\linenumbers
\renewcommand{\arraystretch}{1.2}
%\graphicspath{ {./figures/} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{
S.~R.~Hinton\altaffilmark{1},
T.~M.~Davis\altaffilmark{1},
A.~G.~Kim\altaffilmark{2},
D.~Brout\altaffilmark{3},
C.~B.~D'Andrea\altaffilmark{3},
R.~Kessler\altaffilmark{4,5},
J.~Lasker\altaffilmark{4,5},
C.~Lidman\altaffilmark{6},
E.~Macaulay\altaffilmark{7},
A.~M\"oller\altaffilmark{8,6},
M.~Sako\altaffilmark{3},
D.~Scolnic\altaffilmark{5},
M.~Smith\altaffilmark{9},
R.~C.~Wolf\altaffilmark{10},
S.~Allam\altaffilmark{11},
J.~Annis\altaffilmark{11},
S.~Avila\altaffilmark{7},
E.~Bertin\altaffilmark{12,13},
D.~Brooks\altaffilmark{14},
D.~L.~Burke\altaffilmark{15,16},
A.~Carnero~Rosell\altaffilmark{17,18},
M.~Carrasco~Kind\altaffilmark{19,20},
J.~Carretero\altaffilmark{21},
M.~Childress\altaffilmark{9},
C.~E.~Cunha\altaffilmark{15},
L.~N.~da Costa\altaffilmark{18,22},
C.~Davis\altaffilmark{15},
J.~De~Vicente\altaffilmark{17},
D.~L.~DePoy\altaffilmark{23},
P.~Doel\altaffilmark{14},
T.~F.~Eifler\altaffilmark{24,25},
B.~Flaugher\altaffilmark{11},
P.~Fosalba\altaffilmark{26,27},
J.~Frieman\altaffilmark{11,5},
J.~Garc\'ia-Bellido\altaffilmark{28},
E.~Gaztanaga\altaffilmark{26,27},
D.~W.~Gerdes\altaffilmark{29,30},
R.~A.~Gruendl\altaffilmark{19,20},
J.~Gschwend\altaffilmark{18,22},
G.~Gutierrez\altaffilmark{11},
W.~G.~Hartley\altaffilmark{14,31},
D.~L.~Hollowood\altaffilmark{32},
K.~Honscheid\altaffilmark{33,34},
E.~Krause\altaffilmark{24},
K.~Kuehn\altaffilmark{35},
N.~Kuropatkin\altaffilmark{11},
O.~Lahav\altaffilmark{14},
M.~Lima\altaffilmark{36,18},
M.~A.~G.~Maia\altaffilmark{18,22},
M.~March\altaffilmark{3},
J.~L.~Marshall\altaffilmark{23},
F.~Menanteau\altaffilmark{19,20},
R.~Miquel\altaffilmark{37,21},
E.~Morganson\altaffilmark{20},
R.~L.~C.~Ogando\altaffilmark{18,22},
A.~A.~Plazas\altaffilmark{25},
E.~Sanchez\altaffilmark{17},
V.~Scarpine\altaffilmark{11},
R.~Schindler\altaffilmark{16},
M.~Schubnell\altaffilmark{30},
S.~Serrano\altaffilmark{26,27},
I.~Sevilla-Noarbe\altaffilmark{17},
M.~Soares-Santos\altaffilmark{38},
F.~Sobreira\altaffilmark{39,18},
E.~Suchyta\altaffilmark{40},
G.~Tarle\altaffilmark{30},
D.~Thomas\altaffilmark{7},
V.~Vikram\altaffilmark{41},
and Y.~Zhang\altaffilmark{11}
\\ \vspace{0.2cm} (DES Collaboration) \\
}

\affil{$^{1}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia}
\affil{$^{2}$ Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA}
\affil{$^{3}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA}
\affil{$^{4}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA}
\affil{$^{5}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}
\affil{$^{6}$ The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia}
\affil{$^{7}$ Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK}
\affil{$^{8}$ ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}
\affil{$^{9}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK}
\affil{$^{10}$ Graduate School of Education, Stanford University, 160, 450 Serra Mall, Stanford, CA 94305, USA}
\affil{$^{11}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}
\affil{$^{12}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France}
\affil{$^{13}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France}
\affil{$^{14}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK}
\affil{$^{15}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA}
\affil{$^{16}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
\affil{$^{17}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain}
\affil{$^{18}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\affil{$^{19}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA}
\affil{$^{20}$ National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA}
\affil{$^{21}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain}
\affil{$^{22}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\affil{$^{23}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA}
\affil{$^{24}$ Department of Astronomy/Steward Observatory, 933 North Cherry Avenue, Tucson, AZ 85721-0065, USA}
\affil{$^{25}$ Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA 91109, USA}
\affil{$^{26}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain}
\affil{$^{27}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain}
\affil{$^{28}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain}
\affil{$^{29}$ Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}
\affil{$^{30}$ Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA}
\affil{$^{31}$ Department of Physics, ETH Zurich, Wolfgang-Pauli-Strasse 16, CH-8093 Zurich, Switzerland}
\affil{$^{32}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA}
\affil{$^{33}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA}
\affil{$^{34}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA}
\affil{$^{35}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia}
\affil{$^{36}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil}
\affil{$^{37}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain}
\affil{$^{38}$ Brandeis University, Physics Department, 415 South Street, Waltham MA 02453}
\affil{$^{39}$ Instituto de F\'isica Gleb Wataghin, Universidade Estadual de Campinas, 13083-859, Campinas, SP, Brazil}
\affil{$^{40}$ Computer Science and Mathematics Division, Oak Ridge National Laboratory, Oak Ridge, TN 37831}
\affil{$^{41}$ Argonne National Laboratory, 9700 South Cass Avenue, Lemont, IL 60439, USA}

@@

As we are focused on the spectroscopically confirmed supernovae for this iteration of the method, we assume the observed redshift $\hat{z}$ is the true redshift $z$ such that $P(\hat{z}|z) = \delta(\hat{z} - z)$. Potential sources of redshift error (such as peculiar velocities) are taken into account not via uncertainty on redshift (which is technically challenging to implement {\blue as varying redshifts introduce computational complexity in computing the distance modulus integral}) but instead uncertainty on distance modulus. Similarly, we take the mass probability estimate $\hat{m}$ as correct, and do not model a latent variable to represent uncertainty on the probability estimate. One of the strengths of {\steve} (and the {\rubin} analysis) is that for future data sets where supernovae have been classified photometrically, and we expect some misclassification and misidentification of the host galaxies, these misclassifications can naturally be modelled and taken into account by introducing additional populations that supernovae have a non-zero probability of belonging to.

\begin{deluxetable}{ll}
	\tablecolumns{2}
	\tablewidth{0.99\columnwidth}
	\tablecaption{Model Parameters}
	\tablehead { \colhead{Parameter} & \colhead{Description} }
	\startdata

	&\textbf{Global Parameters} \\

	$\Omega_m$  & Matter density  \\
	$w$  &  Dark energy equation of state  \\
	$\alpha$ & Stretch standardisation   \\
	$\beta$         &  color standardisation   \\
	$\delta(0)$ & Scale of the mass-magnitude correction\\
	$\delta(\infty)/\delta(0)$ & Redshift-dependence of mass-magnitude correction\\
	$\delta\mathcal{Z}_i$ & Systematics scale\\
	$\langle M_B \rangle$ & Mean absolute magnitude \\
	\\
	& \textbf{Survey Parameters} \\

	$\delta S$ & Selection effect deviation \\
	$\langle x_1^i \rangle$ & Mean stretch nodes\\
	$\langle c^i \rangle$ & Mean color nodes\\
	$\alpha_c$ & Skewness of color population \\
	$\sigma_{M_B}$ & Population magnitude scatter \\
	$\sigma_{x_1}$ & Population stretch scatter \\
	$\sigma_{c}$ & Population color scatter \\
	$\kappa_{0}$ & Extra color dispersion\\
	$\kappa_{1}$ & Redshift-dependence of extra color dispersion\\
	\\
	& \textbf{Supernova Parameters} \\
	$m_B$ & True flux\\
	$x_1$ & True stretch \\
	$c$ & True color \\
	$z$ & True redshift \\	
	$M_B$ & Derived absolute magnitude \\
	$\mu$ & Derived distance modulus \\
	\\
	& \textbf{Input Data}\tablenotemark{a} \\

	$\hat{m}_B$ & Measured flux\\
	$\hat{x}_1$ & Measured stretch \\
	$\hat{c}$ & Measured color \\
	$C$ & Covariance on flux, stretch and color \\
	$\hat{z}$ & Observed redshift \\
	$\hat{m}$ & Determined mass probability \\
	$\hat{p}$ & Determined Ia probability \\
	\enddata
	\tablenotetext{a}{Not model parameters but shown for completeness.}
\label{tab:param_summary}
\end{deluxetable}

@@

 \begin{figure}
 	\begin{center}
 		\includegraphics[width=\columnwidth]{tikz-figure0.pdf}
 	\end{center}
 	\caption{Probabilistic graphical model for our likelihood. Double-lined nodes represent observed variables, diamond nodes represent deterministic variables, single-lined ellipse nodes represent fit variables. The SN box represents observed variables and latent variables for each individual supernova, whilst the survey box represents survey-specific variables, which in general describe the supernova population for the survey and the systematics associated with it. Variables that appear outside both boxes represent top level model parameters.}
 	\label{fig:pgm}
 \end{figure}

@@

Unlike many previous formalisms which utilise $M_B$ as a singular number and model magnitude scatter on the apparent magnitude $m_B$, we incorporate this scatter into the underlying rest-frame population by having a population in absolute magnitude space. {\blue This is mathematically equivalent, however allows us to model the underlying population and intrinsic scatter distinctly.} To denote this difference, we refer to the mean of our absolute magnitude population with $\langle M_B \rangle$.

In addition to absolute magnitude, the underlying supernova population is also characterised by distributions in color and stretch. We follow the prior work of {\rubin} and model the color population as an independent redshift-dependent skew normal distribution for each survey. For the stretch population, we adopt a redshift-dependent normal distribution, and magnitude dispersion is modelled as a normal distribution. We also tested a skew-normal approach for these parameters, reverting to the normal distributions as they are computationally easier to evaluate and we found no reduction in cosmological bias with the skew-normal distributions for stretch and magnitude. Following {\rubin} we allow the mean color and stretch to vary over redshift, anchoring four equally spaced redshift nodes spanning the redshift range of each survey, linearly interpolating between the nodes to determine the mean stretch and color for a given redshift. These nodes are represented as $\langle x_1^i \rangle$ and $\langle c^i \rangle$. Both the color and stretch means are modelled with normal priors. Initial versions of our model adopted a fully covariant multivariate skew normal (with skewness set to zero only for the magnitude component) to capture correlations between $m_B$ and $c$, however pathological fitting complications required us to simplify our treatment. We parametrise the color skewness $\alpha_c$ by sampling $\delta_c = \alpha_c / \sqrt{1 + \alpha_c^2}$ which itself is given a uniform prior $\mathcal{U}(0,0.98)$ that allows $\alpha_c$ to span positive values in the realm of physical plausibility as determined from constraints in \citet{Scolnic2016}. We sample $\delta_c$ in log space for efficiency in sampling close to zero. The width of the population, represented by the vector $\lbrace \sigma_{M_B}, \sigma_{x_1}, \sigma_c \rbrace$ is subject to Cauchy priors with {\blue mean 0 and width 1}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[twocolumn,trackchanges,tighten]{aastex62}

@@

%\usepackage{lineno}
%\linenumbers
%\graphicspath{ {./figures/} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{S.~R.~Hinton}
\affiliation{School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia}
\author{T.~M.~Davis}
\affiliation{School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia}
\author{A.~G.~Kim}
\affiliation{Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA}
\author{D.~Brout}
\affiliation{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA}
\author{C.~B.~D'Andrea}
\affiliation{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA}
\author{R.~Kessler}
\affiliation{Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA}
\affiliation{Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}
\author{J.~Lasker}
\affiliation{Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA}
\affiliation{Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}
\author{C.~Lidman}
\affiliation{The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia}
\author{E.~Macaulay}
\affiliation{Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK}
\author{A.~M\"oller}
\affiliation{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}
\affiliation{The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia}
\author{M.~Sako}
\affiliation{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA}
\author{D.~Scolnic}
\affiliation{Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}
\author{M.~Smith}
\affiliation{School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK}
\author{R.~C.~Wolf}
\affiliation{Graduate School of Education, Stanford University, 160, 450 Serra Mall, Stanford, CA 94305, USA}
\author{M.~Childress}
\affiliation{School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK}
\author{E.~Morganson}
\affiliation{National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA}
\author{S.~Allam}
\affiliation{Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}
\author{J.~Annis}
\affiliation{Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}
\author{S.~Avila}
\affiliation{Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK}
\author{E.~Bertin}
\affiliation{CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France}
\affiliation{Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France}
\author{D.~Brooks}
\affiliation{Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK}
\author{D.~L.~Burke}
\affiliation{Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA}
\affiliation{SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
\author{A.~Carnero~Rosell}
\affiliation{Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain}
\affiliation{Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\author{M.~Carrasco~Kind}
\affiliation{Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA}
\affiliation{National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA}
\author{J.~Carretero}
\affiliation{Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain}
\author{C.~E.~Cunha}
\affiliation{Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA}
\author{L.~N.~da Costa}
\affiliation{Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\affiliation{Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\author{C.~Davis}
\affiliation{Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA}
\author{J.~De~Vicente}
\affiliation{Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain}
\author{D.~L.~DePoy}
\affiliation{George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA}
\author{P.~Doel}
\affiliation{Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK}
\author{T.~F.~Eifler}
\affiliation{Department of Astronomy/Steward Observatory, 933 North Cherry Avenue, Tucson, AZ 85721-0065, USA}
\affiliation{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA 91109, USA}
\author{B.~Flaugher}
\affiliation{Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}
\author{P.~Fosalba}
\affiliation{Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain}
\affiliation{Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain}
\author{J.~Frieman}
\affiliation{Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}
\affiliation{Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}
\author{J.~Garc\'ia-Bellido}
\affiliation{Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain}
\author{E.~Gaztanaga}
\affiliation{Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain}
\affiliation{Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain}
\author{D.~W.~Gerdes}
\affiliation{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}
\affiliation{Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA}
\author{R.~A.~Gruendl}
\affiliation{Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA}
\affiliation{National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA}
\author{J.~Gschwend}
\affiliation{Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\affiliation{Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\author{G.~Gutierrez}
\affiliation{Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}
\author{W.~G.~Hartley}
\affiliation{Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK}
\affiliation{Department of Physics, ETH Zurich, Wolfgang-Pauli-Strasse 16, CH-8093 Zurich, Switzerland}
\author{D.~L.~Hollowood}
\affiliation{Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA}
\author{K.~Honscheid}
\affiliation{Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA}
\affiliation{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}
\author{E.~Krause}
\affiliation{Department of Astronomy/Steward Observatory, 933 North Cherry Avenue, Tucson, AZ 85721-0065, USA}
\author{K.~Kuehn}
\affiliation{Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia}
\author{N.~Kuropatkin}
\affiliation{Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}
\author{O.~Lahav}
\affiliation{Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK}
\author{M.~Lima}
\affiliation{Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil}
\affiliation{Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\author{M.~A.~G.~Maia}
\affiliation{Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\affiliation{Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\author{M.~March}
\affiliation{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA}
\author{J.~L.~Marshall}
\affiliation{George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA}
\author{F.~Menanteau}
\affiliation{Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA}
\affiliation{National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA}
\author{R.~Miquel}
\affiliation{Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain}
\affiliation{Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain}
\author{R.~L.~C.~Ogando}
\affiliation{Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\affiliation{Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\author{A.~A.~Plazas}
\affiliation{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA 91109, USA}
\author{E.~Sanchez}
\affiliation{Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain}
\author{V.~Scarpine}
\affiliation{Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}
\author{R.~Schindler}
\affiliation{SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
\author{M.~Schubnell}
\affiliation{Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA}
\author{S.~Serrano}
\affiliation{Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain}
\affiliation{Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain}
\author{I.~Sevilla-Noarbe}
\affiliation{Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain}
\author{M.~Soares-Santos}
\affiliation{Brandeis University, Physics Department, 415 South Street, Waltham MA 02453}
\author{F.~Sobreira}
\affiliation{Instituto de F\'isica Gleb Wataghin, Universidade Estadual de Campinas, 13083-859, Campinas, SP, Brazil}
\affiliation{Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil}
\author{E.~Suchyta}
\affiliation{Computer Science and Mathematics Division, Oak Ridge National Laboratory, Oak Ridge, TN 37831}
\author{G.~Tarle}
\affiliation{Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA}
\author{D.~Thomas}
\affiliation{Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK}
\author{V.~Vikram}
\affiliation{Argonne National Laboratory, 9700 South Cass Avenue, Lemont, IL 60439, USA}
\author{Y.~Zhang}
\affiliation{Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}

@@

As we are focused on the spectroscopically confirmed supernovae for this iteration of the method, we assume the observed redshift $\hat{z}$ is the true redshift $z$ such that $P(\hat{z}|z) = \delta(\hat{z} - z)$. Potential sources of redshift error (such as peculiar velocities) are taken into account not via uncertainty on redshift (which is technically challenging to implement \added{as varying redshifts introduce computational complexity in computing the distance modulus integral}) but instead uncertainty on distance modulus. Similarly, we take the mass probability estimate $\hat{m}$ as correct, and do not model a latent variable to represent uncertainty on the probability estimate. One of the strengths of {\steve} (and the {\rubin} analysis) is that for future data sets where supernovae have been classified photometrically, and we expect some misclassification and misidentification of the host galaxies, these misclassifications can naturally be modelled and taken into account by introducing additional populations that supernovae have a non-zero probability of belonging to.

\begin{deluxetable}{ll}
	\renewcommand{\arraystretch}{0.8}
	\tablecolumns{2}
	\tablewidth{0.99\columnwidth}
	\tablecaption{Model Parameters}
	\tablehead { \colhead{Parameter} & \colhead{Description} }
	\startdata	
	&\textbf{Global Parameters} \\
	$\Omega_m$  & Matter density  \\
	$w$  &  Dark energy equation of state  \\
	$\alpha$ & Stretch standardisation   \\
	$\beta$         &  color standardisation   \\
	$\delta(0)$ & Scale of the mass-magnitude correction\\
	$\delta(\infty)/\delta(0)$ & Redshift-dependence of mass-magnitude correction\\
	$\delta\mathcal{Z}_i$ & Systematics scale\\
	$\langle M_B \rangle$ & Mean absolute magnitude \\
	\\
	& \textbf{Survey Parameters} \\
	$\delta S$ & Selection effect deviation \\
	$\langle x_1^i \rangle$ & Mean stretch nodes\\
	$\langle c^i \rangle$ & Mean color nodes\\
	$\alpha_c$ & Skewness of color population \\
	$\sigma_{M_B}$ & Population magnitude scatter \\
	$\sigma_{x_1}$ & Population stretch scatter \\
	$\sigma_{c}$ & Population color scatter \\
	$\kappa_{0}$ & Extra color dispersion\\
	$\kappa_{1}$ & Redshift-dependence of extra color dispersion\\
	\\
	& \textbf{Supernova Parameters} \\
	$m_B$ & True flux\\
	$x_1$ & True stretch \\
	$c$ & True color \\
	$z$ & True redshift \\	
	$M_B$ & Derived absolute magnitude \\
	$\mu$ & Derived distance modulus \\
	\\
	& \textbf{Input Data}\tablenotemark{a} \\
	$\hat{m}_B$ & Measured flux\\
	$\hat{x}_1$ & Measured stretch \\
	$\hat{c}$ & Measured color \\
	$C$ & Covariance on flux, stretch and color \\
	$\hat{z}$ & Observed redshift \\
	$\hat{m}$ & Determined mass probability \\
	$\hat{p}$ & Determined Ia probability \\
	\enddata
	\tablenotetext{a}{Not model parameters but shown for completeness.}
\label{tab:param_summary}
\end{deluxetable}

@@

 \begin{figure}
 	\begin{center}
 		\includegraphics[width=\columnwidth]{tikz-figure0.pdf}
 	\end{center}
 	\caption{Probabilistic graphical model for our likelihood. Double-lined nodes represent observed variables, diamond nodes represent deterministic variables, single-lined ellipse nodes represent fit variables. The SN box represents observed variables and latent variables for each individual supernova, whilst the survey box represents survey-specific variables, which in general describe the supernova population for the survey and the systematics associated with it. Variables that appear outside both boxes represent top level model parameters. \added{To solidify that the underlying supernova population lives in $\lbrace M_B, x_1, c\rbrace$ space, we write out the stretch and colour populations along with $M_B$, however note here that those $x_1$ and $c$ values (denoted by an asterix) are identically equal to the $x_1$ and $c$ values in the latent node they are conditioned on, and in the code implementation, they are the same variable.}}
 	\label{fig:pgm}
 \end{figure}

@@

Unlike many previous formalisms which utilise $M_B$ as a singular number and model magnitude scatter on the apparent magnitude $m_B$, we incorporate this scatter into the underlying rest-frame population by having a population in absolute magnitude space. \added{This is mathematically equivalent, however allows us to model the underlying population and intrinsic scatter distinctly.} To denote this difference, we refer to the mean of our absolute magnitude population with $\langle M_B \rangle$.

In addition to absolute magnitude, the underlying supernova population is also characterised by distributions in color and stretch. We follow the prior work of {\rubin} and model the color population as an independent redshift-dependent skew normal distribution for each survey. For the stretch population, we adopt a redshift-dependent normal distribution, and magnitude dispersion is modelled as a normal distribution. We also tested a skew-normal approach for these parameters, reverting to the normal distributions as they are computationally easier to evaluate and we found no reduction in cosmological bias with the skew-normal distributions for stretch and magnitude. Following {\rubin} we allow the mean color and stretch to vary over redshift, anchoring four equally spaced redshift nodes spanning the redshift range of each survey, linearly interpolating between the nodes to determine the mean stretch and color for a given redshift. These nodes are represented as $\langle x_1^i \rangle$ and $\langle c^i \rangle$. Both the color and stretch means are modelled with normal priors. Initial versions of our model adopted a fully covariant multivariate skew normal (with skewness set to zero only for the magnitude component) to capture correlations between $m_B$ and $c$, however pathological fitting complications required us to simplify our treatment. We parametrise the color skewness $\alpha_c$ by sampling $\delta_c = \alpha_c / \sqrt{1 + \alpha_c^2}$ which itself is given a uniform prior $\mathcal{U}(0,0.98)$ that allows $\alpha_c$ to span positive values in the realm of physical plausibility as determined from constraints in \citet{Scolnic2016}. We sample $\delta_c$ in log space for efficiency in sampling close to zero. The width of the population, represented by the vector $\lbrace \sigma_{M_B}, \sigma_{x_1}, \sigma_c \rbrace$ is subject to Cauchy priors \added{with mean 0 and width 1, following recommendations from the Stan user guide}.
